Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-03 article.tex
Rewrite biosimulators and PYthon

Several tools already exist to \emph{define}, \emph{translate} and \emph{solve} \acp{CRN}.
BioSimulators.org \cite{shaikhBioSimulatorsCentralRegistry2022},
a registry of simulation tools,
lists at least 15 Python software including
COPASI \cite{hoopsCOPASICOmplexPAthway2006},
Tellurium \cite{choiTelluriumExtensiblePythonbased2018} and
PySB \cite{lopezProgrammingBiologicalModels2013}.
COPASI is a standalone software with a \ac{GUI}
that is widely used for its user-friendly interface and comprehensive features.
It also includes Python bindings \cite{bergmannBASICOSimplifiedPython2023b} that allow advanced scripting.
Tellurium is a Python-based modeling environment
that uses a C++ library called libRoadRunner in the backend to translate and solve models.
PySB is a Python library that created a \ac{DSL} using standard Python to define models,
which are then translated to \acp{ODE} using a Perl library called BioNetGen \cite{harrisBioNetGenAdvancesRulebased2016}.

>>>>

Several tools already exist to \emph{define}, \emph{translate} and \emph{solve} \acp{CRN}.
BioSimulators.org \cite{shaikhBioSimulatorsCentralRegistry2022},
a registry of simulation tools,
lists at least 15 softwares categorized under Python including
COPASI \cite{hoopsCOPASICOmplexPAthway2006},
Tellurium \cite{choiTelluriumExtensiblePythonbased2018} and
PySB \cite{lopezProgrammingBiologicalModels2013}.
COPASI is a standalone software with a \ac{GUI}
that is widely used for its user-friendly interface and comprehensive features.
It also includes Python bindings \cite{bergmannBASICOSimplifiedPython2023b} that allow advanced scripting.
Tellurium is a Python-based modeling environment
that uses a C++ library called libRoadRunner in the backend to translate and solve models.
PySB is a Python library that created a \ac{DSL} using standard Python to define models,
which are then translated to \acp{ODE} using a Perl library called BioNetGen \cite{harrisBioNetGenAdvancesRulebased2016}.
